---
title: "ITNS Chapter 00: Preface"
author: "Peter Baumgartner"
date: "`r Sys.Date()`"
bibliography: "www/references.bib"
link-citations: true
editor_options:
  markdown:
    wrap: 72
    references: 
      location: block
    canonical: true

output: 
    learnr::tutorial:
        progressive: true
        allow_skip: true
        theme: "cerulean"
        css: "css/style.css"
runtime: shiny_prerendered
---

```{r setup, echo=F, message=F, warning=F, include=F}
library(tidyverse)
library(DT)
library(learnr)
library(itns)
library(usethis)
tutorial_options(exercise.cap = "Sandbox")
demo_data <- pen_laptop2
```

```{=html}
<!-- <style type="text/css"> -->
<!-- @import url("https://stackpath.bootstrapcdn.com/bootstrap/4.4.1/css/bootstrap.min.css"); -->
<!-- </style> -->
```
## Welcome!

[![Cover image of 'Introduction to the New Statistics' with overlaid
text referencing to unofficial interactive tutorials accompanying the
text
book](images/cover-itns-unofficial-min.png "Cover image with overlaid text"){.float-right
width="250"
height="375"}](https://www.routledgetextbooks.com/textbooks/9781138825529/)

These tutorials support and accompany your working with the textbook
[Introduction to the New
Statistics](https://www.routledgetextbooks.com/textbooks/9781138825529/)
by Geoff Cumming and Robert Calin-Jageman or for short `itns`
[@cumming_introduction_2017].

Here in the preface, we will explain the structure and the different
parts of the interactive website. Additionally, we will also expose you
to some scientifically-based learning strategies.[^1]

[^1]: Another Footnote

## Learning Outcomes

We will start every chapter with [Learning
Outcomes](https://teaching.utoronto.ca/teaching-support/course-design/developing-learning-outcomes/what-are-learning-outcomes/)
(LOs). In principle, LOs are just statements about what students should
be able to do by the end of a learning module (lecture, course, chapter
of a book, degree course, etc.). To accommodate the appropriate level,
LOs have to be stated on different levels of abstraction. To evade
losing overview and drowning in too many different skills, a limitation
to three to five LOs is recommendable.

The crux is to formulate LOs in a way that they can be verified. So they
should use verbs for activities that can be observed. Instead of "can
understand" or "knows," it is better to say "can explain" or "can give
examples," etc.

After completing this preliminary chapter successfully, you should be
able ...

-   to navigate effectively through the tutorials with their different
    type of exercises
-   taking (H5P Cornell) notes effectively to support sustainable
    learning
-   writing take-home messages (with the help of the provided H5P
    Documentation Tool)

At the end of all chapters, we provide a template to judge how well you
have met these objectives.

## Supportive Pedagogy

Under this heading, you will find in the book (p.XX) explanations of the
different formatting items and their purpose. This website has other
possibilities; therefore, we need to present the equivalents we have
chosen.

### Take-home messages

As in the book, each chapter of the interactive tutorials starts with
pointers to what it contains and closes with summary take-home messages.
But this summary is an interactive exercise where you have to choose
from different key messages. At the end of this selection process, you
will get a list of the same take-home messages as presented in the book.
Sometimes our invented wrong alternatives ("distractors") are silly, and
it is clear which answer you have to choose. But even so, you have to
read the different options carefully and make your decision. Selecting
the correct answer is some engagement and better than just scan the text
without a mindful decision.

From a technical perspective, we will offer the H5P content type
[Summary](https://h5p.org/summary). You will find the first example of
the interactive realization of the take-home message at the end of this
chapter.

### Pause, reflect, and discuss

Educational research shows that elaborating on learning material is an
effective learning technique. The book encourages on regular intervals
critical thinking with questions suitable for reflection and discussion.

With these tutorials, we offer [Cornell
Notes](https://lsc.cornell.edu/how-to-study/taking-notes/cornell-note-taking-system/)
as a tool to process and elaborate conveyed information. It supports
learning with a three-part structure of note-taking:

1.  Take notes from a lecture, book, audio, or video. But not in a
    mechanical descriptive way, but decide what is essential and choose
    your own wording.
2.  After you wrote this excerpt, look for cues and key points.
    Formulate problems, generate questions, and write them into another
    text field.
3.  Finally, in the third field, write down your learnings as a summary
    and try a conclusion.

Again we provide this learning tool via an H5P content type. Try it out
and learn about Cornell Notes by taking [✏️Cornell Notes].

### Key terms

The book has vital terms set off from the text and defined in the
glossary at the book's end. Here we use the advantages of an interactive
online tutorial.

You will find [Flash Cards
exercises](https://routledgetextbooks.com/textbooks/9781138825529/student.php)
at the book's website for the terms and expressions used in the book. In
these tutorial files, we add three other types of activities:

-   **Glossary** realized with [H5P
    Accordion](https://h5p.org/accordion).
-   **Drag Text** realized with [H5P Drag the
    Words](https://h5p.org/drag-the-words).
-   **Fill Gap** realized with [H5P Fill in the
    Blanks](https://h5p.org/fill-in-the-blanks).

These three types of exercises represent different levels of difficulty:
Read, remember, recall.

Additionally, we will experiment with [H5P
Crossword](https://www.olivertacke.de/labs/2020/11/19/some-things-take-time-h5p-crossword/)[^2]
and [H5P Memory Game](https://h5p.org/memory-game).

[^2]: This content type is new and yet not released officially.

### Exercises

We have converted the book's review questions with the H5P Question Set
into a collection of interactive exercises. Corresponding to the
subject, we use appropriate question formats like Single and Multiple
Choice, True and False Questions, and other -- partly already mentioned
-- activity types.

In the book, there are two types of exercises: In-text-exercises and
end-of-chapter-exercises.

#### In-Text-Exercises

The book uses primarily ESCI, a specially prepared Exploratory Software
for Confidence Intervals. We complement this important educational
device with practical tutorials to grasp the essentials of
[R](https://www.r-project.org/), "a free software environment for
statistical computing and graphics. It compiles and runs on a wide
variety of UNIX platforms, Windows and macOS."

Learning R to do statistics and data science is a trendy and valuable
professional skill in the job market. We wrote this accompanying book to
ITNS entirely in R, which shows its solid and powerful ecosystem. The
in-text-exercises use `learnr` and `gradethis`, two R packages
specialized tutoring data science and the R Language. So it is a kind of
learning R through R.

To give you a first impression of the tutorial environment, experiment
with `learnr`, the R tutorial software we war using. Head over to the
section [🆁Sandbox Experiments].

#### End-of-Chapter-Exercises

We will explain with this guided tutorial all in-text-exercises and also
give some guided exercises to try for yourself. So you will learn the
basic structure of R and how to use it.

The end-of-chapter-exercises will go even one step farther. We invite
you to practice R inside a modern IDE (Integrated Development
Environment). For this real-world experience, you have to install R and
RStudio, to install and load necessary packages and data sets.

We recommend urgently that you should try to find the solution on your
own. Only when you are exhausted and could not solve the problem, then
consult our solution. Have a look at it, try to understand it, close our
demonstration and try it yourself in your R installation.

### Formatting

For outline paragraphs that deserve special attention, we are using
colored boxes with icons.

::: {.infobox}
<strong>Info:</strong> We use infoboxes as visual markers highlighting
key issues and points. It makes it easier for readers to gain an
overview and find critical points when reviewing for exams.
:::

::: {.warningbox}
<strong>Warning:</strong> We use warning boxes whenever we explain
important cautions that students always need to keep in mind, including
troubles with the meaning of "significance" and what p values can and
cannot tell us.
:::

::: {.stopbox}
<strong>Stop:</strong> We use stop boxes to highlight common pitfalls or
things to watch out for. We hope these will help students avoid making
such errors.
:::

#### Typography

To facilitate your navigation around the tutorial, we have marked the
section header:

-   🧩 Exercise section: Contains puzzle, quiz, tests, etc.

-   ✏️ Rethink and reflect exercises

-   🆁 Guided R tutorials (In-chapter-exercises and more)

-   📊 Solutions (End-of-chapter-exercises)

-   🌐 A collection of internet resources

Package names are in bold text (e.g., **rmarkdown**), and inline code
and filenames are formatted in a typewriter font (e.g.,
`knitr::knit('foo.Rmd'))`. Function names are followed by parentheses
(e.g., `bookdown::render_book())`. The double-colon operator :: means
accessing an object from a package.

## Additional Resources

On the [book's
website](https://routledgetextbooks.com/textbooks/9781138825529/), you
will find [resources for
students](https://routledgetextbooks.com/textbooks/9781138825529/student.php).
It includes:

-   Flashcards exercises
-   Videos
-   Data sets for in-text-exercises
-   Data sets for end-of-chapter-exercises
-   ESCI download
-   Software Guide

You are welcome to use everything, but except for the flashcards
exercises and the ESCI software, this tutorial will use these resources
in a particular way:

-   **Video**: We have added to the videos interactivity: Questions,
    Quizzes, etc.

-   **Data sets**: They are included in the R package `itns`. In the
    tutorial, you will learn how to get this package and use the data
    files.

-   **Software Guide**: Our tutorial will explain how to install and use
    the software.

So for videos, data sets, and software is no need to worry. We will
cover how to get and use these resources at the appropriate places in
the tutorial.

## 🧩Making the most of these tutorials

The main reason for us to write these tutorials is to support your
learning. We hope that the multitude of different exercises invites you
to try them. It is not necessary to take them all, and you can certainly
change our proposed order. The only sequence you should follow: Read
first the corresponding part in the book because the exercises build on
the book's content. They give you feedback, clarify things and practice
your skill, but they are not the primary teaching material.

We wish that the exercises not only foster your learning but are also
enjoyable. We aim to seduce you to stretch your involvement time with
statistics and R. The exercises are therefore not graded, have no time
constraint, and you can repeat them how often you like.

### Learning techniques

Before we are going to talk about learning strategies, try the following
multiple-choice exercise.

<iframe src="https://peter.baumgartner.name/wp-admin/admin-ajax.php?action=h5p_embed&amp;id=339" width="960" height="615" frameborder="0" allowfullscreen="allowfullscreen" title="itns-00: Learning Techniques">

</iframe>

```{=html}
<script src="https://peter.baumgartner.name/wp-content/plugins/h5p/h5p-php-library/js/h5p-resizer.js" charset="UTF-8"></script>
```
So the gist of this exercise is a well established difference in our
brain: To repeat and recall is less effective than retrieve and
reproduce. Understanding is much more than just memorizing. You need to
link new facts or concepts with already established notions so that they
are sustainable anchored in your neuron network.

### Multiple representation

To internalize and grasp new terms and ideas it is necessary to vary the
context of thought and perception. Cognitive science has proofed that
multiple representation is especially well suited for complex scientific
concepts:[^3]

[^3]: Fußnote

> When people are learning complicated scientific concepts, interacting
> with multiple forms of representation such as diagrams, graphs and
> equations can bring unique benefits. [@ainsworth_educational_2008]

We will foster you understanding by presenting the same content varied
in different forms, as text, graphics and video. It's not just that we
expose you passively to the material but we call for your active
engagement with the content by posing puzzles and challenges.
[@ainsworth_functions_1999]

## 🆁Sandbox Experiments

### Demo: Use R as a calculator

```{r demo1, exercise=TRUE}
## use R as simple calculator: try also -,*,/
1 + 1
```

### Demo: Use R functions for statistical calculation

```{r demo2, exercise=TRUE}
## use R functions for statistical computations
## see also 'hint' to try other functions
mean(c(12.1, 6.5, 8.1, 7.6, 12.2, 10.8, 1.0, 2.9, 14.4, 8.4))
```

```{r demo2-hint}
## try instead of mean: median, min, max
## for example
median(c(12.1, 6.5, 8.1, 7.6, 12.2, 10.8, 1.0, 2.9, 14.4, 8.4))

```

### Demo: Use R to inspect data interactively

```{r demo3, exercise=TRUE}
## inspect data: try the different interface elements
datatable(demo_data)
```

### Demo: Use R to visualize data

```{r demo4, exercise=TRUE}
## use R to visualize data
## use 'hint' to change data presentation
ggplot(demo_data, aes(x = transcription)) +
            geom_histogram()

```

```{r demo4-hint}
## try instead of geom_histogram: geom_dotplot, geom_boxplot
## for example
ggplot(demo_data, aes(x = transcription)) +
            geom_dotplot()

```

## ✏️Cornell Notes

Learn what Cornell Notes are and how you can make use of it.

<iframe src="https://peter.baumgartner.name/wp-admin/admin-ajax.php?action=h5p_embed&amp;id=340" width="960" height="771" frameborder="0" allowfullscreen="allowfullscreen" title="Learn about Cornell Notes using Cornell Notes">

</iframe>

```{=html}
<script src="https://peter.baumgartner.name/wp-content/plugins/h5p/h5p-php-library/js/h5p-resizer.js" charset="UTF-8"></script>
```
## 🌐More on Cornell Notes

If you are interested in this kind of note-taking system, here are some
pointers to additional resources on the internet.

<iframe class="wakeletEmbed" width="100%" height="760px" src="https://embed.wakelet.com/wakes/EpM_ssAgvCQ6YSH-JqMJv/list" style="border: none" allow="autoplay">

</iframe>

<!-- Please only call https://embed-assets.wakelet.com/wakelet-embed.js once per page -->

```{=html}
<script src="https://embed-assets.wakelet.com/wakelet-embed.js" charset="UTF-8"></script>
```
## References

[@anderson2002]
